Concurrent Programming with CXL

### 2020-06-08 book/paper.tex
Fixed reference
Latest

\begin{code} 
\begin{verbatim} 
def wait(c):
    call V &(mutex);
    call P c;
;
def signal(c):
    call V c;
    call P &(mutex);
;
\end{verbatim} 
\end{code}

@@

\begin{figure}
\begin{center}
\includegraphics[width=6in]{figures/monitor.jpeg}
\end{center}
\caption{High-level depictions of Hoare and Mesa monitors.  The hall is
where processes wait to enter the bathroom (the critical section).  The
bedrooms illustrate two condition variables.  The circles are processes.}
\label{fig:pc}
\end{figure}

Figure~\ref{fig:bathroom} illustrates the difference with a drawing.
Here a bathroom represents the critical section, allowing only one
process at a time say.  The bedrooms represent condition variables.
There is some condition associated with each bedroom.
In the hall are processes waiting to enter the critical section.

@@

\begin{figure}
\begin{code}
\begin{verbatim}
def Condition(lk):
    result = dict{ .lock: lk, .waiters: {} };
;
def wait(c):
    let lk = (^c).lock, blocked = True:
        (^c).waiters = (^c).waiters + { nametag() };
        ^lk = False;
        while blocked:
            atomic:
                if (not (^lk)) and (not ((nametag()) in (^c).waiters)):
                    ^lk = True;
                    blocked = False;
                ;
            ;
        ;
    ;
;
def notify(c):
    let waiters = (^c).waiters:
        if waiters != {}:
            (^c).waiters = waiters - { choose(waiters) };
        ;
    ;
;
def notifyAll(c):
    (^c).waiters = {};
;
\end{verbatim}
\end{code}
\caption{Implementation of condition variables in the \texttt{synch} module.}
\label{fig:cv}
\end{figure}

>>>>

\begin{code} 
\begin{Verbatim}[xleftmargin=5mm,numbers=left]
def wait(c):
    call V &(mutex);
    call P c;
;
def signal(c):
    call V c;
    call P &(mutex);
;
\end{Verbatim} 
\end{code}

@@

\begin{figure}
\begin{center}
\includegraphics[width=6in]{figures/monitor.jpeg}
\end{center}
\caption{High-level depictions of Hoare and Mesa monitors.  The hall is
where processes wait to enter the bathroom (the critical section).  The
bedrooms illustrate two condition variables.  The circles are processes.}
\label{fig:monitors}
\end{figure}

Figure~\ref{fig:monitors} illustrates the difference with a drawing.
Here a bathroom represents the critical section, allowing only one
process at a time say.  The bedrooms represent condition variables.
There is some condition associated with each bedroom.
In the hall are processes waiting to enter the critical section.

@@

\begin{figure}
\begin{code}
\begin{Verbatim}[xleftmargin=5mm,numbers=left]
import bag;

def Condition(lk):
    result = dict{ .lock: lk, .waiters: bagEmpty() };
;
def wait(c):
    let lk = (^c).lock, blocked = True, cnt = bagCount((^c).waiters, nametag()):
        call bagAdd(&((^c).waiters), nametag());
        ^lk = False;
        while blocked:
            atomic:
                if (not (^lk)) and (bagCount((^c).waiters, nametag()) <= cnt):
                    ^lk = True;
                    blocked = False;
                ;
            ;
        ;
    ;
;
def notify(c):
    atomic:
        let waiters = (^c).waiters:
            if waiters != bagEmpty():
                call bagRemove(&((^c).waiters), bagChoose(waiters));
            ;
        ;
    ;
;
def notifyAll(c):
    (^c).waiters = bagEmpty();
;
\end{Verbatim}
\end{code}
\caption{Implementation of condition variables in the \texttt{synch} module.}
\label{fig:cv}
\end{figure}

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{../RWcv.cxl}
\end{code}
\caption{Unfair Reader/Writer Lock implemtation using Mesa-style condition variables.}
\label{fig:RWcv}
\end{figure}
